\documentclass[letterpaper,10pt]{article}

\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{hyperref}
\usepackage{tocloft}
\usepackage{array}
\definecolor{dgray}{gray}{0.4}
\hypersetup{
  colorlinks=true,
  urlcolor=dgray
}

\usepackage[xetex]{graphicx}
\usepackage{fontspec,xunicode}
\usepackage[
top    = 2.75cm,
bottom = 2.75cm,
left   = 3.00cm,
right  = 2.50cm]{geometry}
\geometry{paperwidth=8.5in, paperheight=13.5in}

\defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}


\setlength{\outerbordwidth}{2pt}
\definecolor{shadecolor}{gray}{0.40}
\definecolor{shadecolorB}{gray}{0.90}


\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
%\setlength{\paperheight}{12in}
%\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{12in}
\setlength{\textwidth}{7in}
%\setlength{\topmargin}{-0.8in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{2pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{2pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.83in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Sudhanshu Bahety}  
&D-212,HJB Hall of Residence\\ 
UG (4th year), Computer Science and Engineering
& Kharagpur, India, PIN-721306\\
Indian Institute of Technology Kharagpur& \href{mailto:bahetysudhanshu@gmail.com}{bahetysudhanshu@gmail.com}\\
\end{tabular*}
\\[-10pt]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular*}{7in}{ c @{\extracolsep{\fill} } c @{\extracolsep{\fill} } c @{\extracolsep{\fill} } r }
\textbf{Degree/Examination}  & \textbf{Institution}  & \textbf{Year}  & \textbf{Grade}   \\
\hline \\ [-1.5ex]
B.Tech(upto $6^{th}$ semester)  & Indian Institute Of Technology,Kharagpur &  2012-2016  & CGPA - 9.47/10  \\
& & & Rank - 8(Total),6(BTech) \\
\hline \\ [-1.5ex]
High School & Calcutta Boys' School & 2011 & 91.5\% \\
\hline \\ [-1.5ex]
Secondary School & Calcutta Boys' School & 2009 & 90.2\% \\
\hline \\ [-1.5ex]
\end{tabular*}
\\[-10pt]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Relevant Courses Taken}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-10pt}
\begin{tabbing}
Programming and Data Structures \hspace{2cm}\= Algorithms-I \hspace{2cm}\= Algorithms-II \\
Machine Learning\textsuperscript{\#} \> Artificial Intelligence\textsuperscript{\#} \> Natural Language Processing\textsuperscript{\#} \\
Formal Languages and Automata Theory \> Software Engineering\textsuperscript{L} \> Probability and Statistics\\
Computer Organization and Architechture\textsuperscript{L}\> Signals and Systems\textsuperscript{L}\> Switching Circuits and Logic Design\textsuperscript{L}\\
\end{tabbing}
\vspace{-0.60cm}
\hspace{12.5cm} \footnotesize{
\textsuperscript{\#}To be completed before Dec 2015}\\[-5pt]
\vspace{0.10cm}
\hspace{12.6cm} \footnotesize{
\textsuperscript{L}Subject has Lab component}\\[-5pt]

\resheading{Internships}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\large \textbf{Context Aware Media Content Analysis}}\\
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
 \textbf{Mentors: Dr. Shiv Saini, Dr. Atanu Sinha}&Adobe Big Data Intelligence Lab, May - July 2015
\end{tabular*}
\begin{itemize}
\item Studied the patterns of how a media article gets consumed.
\item Developed an Android Application \href{https://play.google.com/store/apps/details?id=com.adobe.atl.proreader&hl=fr_CA}{ProReader} (Available on Play Store) to study media consumption pattern.
\item Made a Linear Regression predictive model to predict the context in which a new media article would get consumed.
\item Implemented the linear regression model in R.\\[10pt]
\end{itemize}
{\large \textbf{Human Activity Recognition}}\\
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
 \textbf{Mentor: Dr. Shiv Saini}&Adobe Big Data Intelligence Lab, May - July 2015
\end{tabular*}
\begin{itemize}
\item Developed an Android Application to collect sensor datas.
\item Analyzed different patterns in data while a person is in different context while reading.
\item Applied machine learning models to estimate the context of the user.\\[10pt]
\end{itemize}

{\large \textbf{Key Management Scheme for Distributed Sensor Networks}}
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
 \textbf{Mentor: Dr. Sushmita Ruj}&Indian Statistical Institute, May - June 2014
\end{tabular*}
\begin{itemize}
\item Studied how the information travels between two nodes within a network.
\item Analyzed how the average degree of nodes,average path length changes if an adversary attacks some nodes in the network.
\item Simulated the above network using networkx in C++.
\end{itemize}
\vspace{-8pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Academic Projects}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\large \textbf{BTech Project : Spam detection in meta-data of YouTube videos}}\\
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
 \textbf{Mentor: Dr. Pawan Goyal}&Jan 2015 - Current
\end{tabular*}
\begin{itemize}
\item Analyzing how spammers post videos with false metadata to increase views and likes of the videos.
\item Analyzing the comments,view,likes/dislikes and other feature associated with the video to tag whether a metadata is false or not.
\item Adapting NLP techniques to get sentiments of the comments and ML techniques to get classify metadata as spam or not spam.\\[10pt]
\end{itemize}

{\large \textbf{Error concealment in videos}}\\
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
 \textbf{Mentor: Avisek Lahiri}&JAugust 2015 - Current
\end{tabular*}
\begin{itemize}
\item Used dlib library to run the face landmark detection alogrithm in live webcam video.
\item Used openCV to run delaunay triangulation on the points present on the face, thereby segmenting the face.
\item Used Matlab to calculate the affine inverse and thus using the previous frames of videos to fill the bad pixels in current frame.\\[10pt]
\end{itemize}

{\large \textbf{Database Management Term Project : IPL Auctioning System}}
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
 \textbf{Mentor: Dr. Pallab Dasgupta and Dr. Animesh Mukherjee}&April 2015
\end{tabular*}
\begin{itemize}
\item Crawled Wikipedia and official IPL websites to get the IPL Auctioning data.
\item System was designed using Java Swing Library.
\item Supported various range queries and standard auctioning queries on the dataset.\\[10pt]
\end{itemize}

{\large \textbf{Complex Network Term Project : Twitter LIWC}}
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
 \textbf{Mentor: Dr. Animesh Mukherjee}&January - April 2015
\end{tabular*}
\begin{itemize}
\item Manually increased the size of categories of LIWC by adding words and emoticons that are used in OSN.
\item Used dictionary to convert out of vocabulary words used in OSN to in vocabulary words.
\item Implemented an algorithm of distributional thesarus to increase the words in each categories.\\[10pt]
\end{itemize}

{\large \textbf{Compilers Term Project :Compiler for tinyC language (a subset of C-language)}}\\
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{Mentor: Dr. Partha Pratim Das} & August 2014-Nov 2014
\end{tabular*}
\begin{itemize}
\item Used flex for lexical analysis and Used yacc for writing the grammar rules and actions.
\item Supported recursive functions.
\end{itemize}
\vspace{5pt}
{\large \textbf{Software Engineering Term Project: Online Sales Portal}}\\
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{Mentor: Dr. Partha Pratim Das} & April 2014
\end{tabular*}
\begin{itemize}
\item Made an GUI Application using Java Swing.
\item The idea was similar to buy and sell products online like eBay,OLX.
\end{itemize}

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Startup}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item Patent Pending (295/KOL/2015): A system and method for range independent tamper proof tracking
\item Finalist at Ideas ’15 Techkriti, Business Plan competition
\item Finalist at Kshitij Business Plan competition, for the most innovative startup idea
\end{itemize}

\vspace{-8pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Achievements in Technical Activites}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{Overnite-2015 Programming Competition (ACM Certified)}  & \textsc{2015} \\
My team Heapify were finalist in the onsite round.\\[5pt]
\textbf{Facebook HackerCup}  & \textsc{2015} \\
Secured a position of 418 in the Round 2, qualified Round 1 with a position of 504\\[5pt]
\textbf{Mozboot Hackathon, Kshitij- IIT Kharagpur}  & \textsc{2014} \\
Won the hackathon organized by \textbf{Mozilla} by making web game of blackjack. I wrote the entire code in JavaScript.\\[5pt]
\textbf{Google Devfest Competition}  & \textsc{2013} \\
Made a mathematical android application game of Nim in which I implemented the front end of the application.\\[5pt]
\textbf{IEEE Certified Image Processing Workshop}  & \textsc{2013} \\
Programmed a Lane Detection Robot to detect path and move accordingly using openCV library in C++.\\
Also, programmed a Shape Detection Robot to identify circle, square, or a triangle.\\[5pt]
\end{tabular*}
\vspace{-8pt}
\resheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{-2pt}
\textbf{Programming Languages :} C, C++, MySQL, Java, Python, R, HTML5, CSS, JavaScript\\
\textbf{IDE :} Eclipse, Netbeans, Android Studio\\
\textbf{Platforms :} Windows, Linux
\vspace{-8pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Extra Curricular Activities}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item Won \textbf{Gold Medal} in Karate at Meerut.(\textbf{Final Round} of All India Karate Competition, 2001)
\item Won \textbf{Bronze Medal} in Karate at Mangalore.(\textbf{Second Round} of All India Karate Competition, 1999)
\item Won \textbf{Bronze Medal} in Karate at Kolkata.(\textbf{First Round} of All India Karate Competition, 1998)
\item Served at National Service Scheme for 2 years, IIT Kharagpur.
\item Taught Freshers basics of Programming and Data Structures using C.
\end{itemize}

\end{document}